The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-10-16 donde.tex
checkpoint before text editing - here all the results are final

\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{align*}

>>>>

\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{align*}

### 2023-10-16 presentation.tex
checkpoint before text editing - here all the results are final

\vspace{.2in}
\: \: \: \: APR: equivalent yearly interest generated by sum of payments:
   \begin{equation*}
    (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{equation*}

>>>>

\vspace{.2in}
\: \: \: \: APR: equivalent yearly interest generated by sum of payments:
   \begin{equation*}
    (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{equation*}
